---
title: "Problem set 1 question 1"
author: "Juntong Lin"
date: '2020-10-02'
output: pdf_document
tags:
- R Markdown
- plot
- regression
categories: R
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Question 1 
# part(a)
```{r}
install.packages("opendatatoronto")
install.packages("devtools")
devtools::install_github("sharlagelfand/opendatatoronto")
devtools::install_github("hodgettsp/cesR")

library(opendatatoronto)
library(cesR)
library(tidyverse)
library(visdat)
library(skimr)
cesR::get_decon()
```
The data is a research of 22 variables, such as citizenship, age and income, for the people on ces2019_web. There are total 37822 observations and 22 variables. The dataset is interesting because the population is large, and various features are researched. Thus I can study the relationship between many different kinds of fields. 

# part(b)
```{r}
decon <- decon %>%  mutate(Age = 100 - as.numeric(decon$yob))
decon %>% filter(income <= 1000000) %>% 
  ggplot(aes(x =Age, y = income)) + geom_point() + theme_bw() + labs(x ="age", y = "income")
```
I made a scatter plot for age and income, with age on the x axis and income on the y axis. From the plot, most of the observations gather under the 250000. This means no matter the age, most of the people have income under 250000. Overall, the plot shows a weak positive linear trend. The age has a weak influence on the income, and as getting older, the average income would increase a little bit.

# part(c)
```{r}
decon %>% group_by(income_cat) %>% summarize(mean_age = mean(Age), median_age = median(Age)) 
```
I found that income generally increase as age increase. Though the age for groups with income more than 30000 fluctuate, the no income group and 1 to 30,000 group is obviously younger. And the highest group has the oldest mean age. 

# part(d)
In this dataset, I was interested in the relationship between the age and income. I estimate that the income will increase as getting older before getting the data. After study the scatter plot, I find that the positive linear relationship is weak, because most of the people at all age range gather under a value. And from the summarize study, the mean age in the middle groups fluctuate a lot. Thus the relationship between this two variables is actually complicated. 

# part(e)
[1] Wickham et al., (2019). Welcome to the tidyverse. Journal of
Open Source Software, 4(43), 1686,
https://doi.org/10.21105/joss.01686

[2] Tierney N (2017). “visdat: Visualising Whole Data Frames.”
_JOSS_, *2*(16), 355. doi: 10.21105/joss.00355 (URL:
https://doi.org/10.21105/joss.00355), <URL:
http://dx.doi.org/10.21105/joss.00355>.

[3]   Elin Waring, Michael Quinn, Amelia McNamara, Eduardo Arino
de la Rubia, Hao Zhu and Shannon Ellis (2020). skimr:
Compact and Flexible Summaries of Data.
https://docs.ropensci.org/skimr (website),
https://github.com/ropensci/skimr.

